---
title: "Where do CDI words come from?"
author: "George & Georgia"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(glue)
library(wordbankr)
require(tidyverse)
require(here)
require(ggrepel)
require(kableExtra)
require(tidyboot)
require(readr)
require(tokenizers)
require(lme4)
require(lmerTest)
require(ggeffects)
require(ggpubr)
library(stringi)
library(arm)

lang <- "French (French)"

wb_data <- readRDS("/Users/loukatou/Documents/booky-cdi/data/french_(french).rds")
uni_lemmas <- read_csv("fr_uni_lemmas.csv")

walk(list.files("*", pattern = "*.R$", full.names = TRUE), source)

```


```{r aoa functions, echo=F, message=F, warning=F}

normalize_language <- function(language) {
  language |> str_replace(" ", "_") |> str_to_lower()
}

lang_map <- read_csv("language_map.csv")

convert_lang_stemmer <- function(lang, method = "snowball") {
  lang_map |> filter(wordbank == lang) |> pull(!!method)
}


fit_bglm <- function(df, max_steps = 200) {
  model <- arm::bayesglm(cbind(num_true, num_false) ~ age,
                         family = "binomial",
                         prior.mean = .3,
                         prior.scale = c(.01),
                         prior.mean.for.intercept = 0,
                         prior.scale.for.intercept = 2.5,
                         prior.df = 1,
                         data = df,
                         maxit = max_steps)
  intercept <- model$coefficients[["(Intercept)"]]
  slope <- model$coefficients[["age"]]
  tibble(intercept = intercept, slope = slope, aoa = -intercept / slope)
}

fit_aoas <- function(wb_data, max_steps = 200, min_aoa = 0, max_aoa = 72) {
  aoas <- wb_data |>
    mutate(num_false = total - num_true) |>
    nest(data = -c(language, measure, uni_lemma)) |>
    mutate(aoas = map(data, fit_bglm)) |>
    dplyr::select(-data) |>
    unnest(aoas) |>
    filter(aoa >= min_aoa, aoa <= max_aoa)
}

fit_aoas_def <- function(wb_data, max_steps = 200, min_aoa = 0, max_aoa = 72) {
  aoas <- wb_data |>
    mutate(num_false = total - num_true) |>
    nest(data = -c(language, measure, definition)) |>
    mutate(aoas = map(data, fit_bglm)) |>
    dplyr::select(-data) |>
    unnest(aoas) |>
    filter(aoa >= min_aoa, aoa <= max_aoa)
}

wb_data_def <- wb_data %>% unnest(items) %>% dplyr::select(-uni_lemma)

aoas_def <- fit_aoas(wb_data_def)
aoas_unilemma <- fit_aoas(wb_data)

#saveRDS(aoas_def, "data/fr_aoas_definition.rds")

```


## Goal

Can we identify words on the CDI that are more bookish, speechy, or from TV? (Controlling for difficulty, as more bookish words are probably more difficult)

Using this distributional source information, can we find features of children (e.g., mother's education) that relate to knowledge of subsets of words (e.g. bookish words)?

To start, we will look at American English, before extending to British English and French.
We will begin with unlemmatized corpora, and disregard part-of-speech classification.



```{r unilemma functions, echo=F, message=F, warning=F}
build_special_case_map <- function(lang) {
  norm_lang <- normalize_language(lang)
  special_case_file <- glue("resources/special_cases/{norm_lang}.csv")
  if (file.exists(special_case_file)) {
    special_case_map <- read_csv(special_case_file, col_names = FALSE) |>
      rename(uni_lemma = X1, definition = X2) |>
      pivot_longer(-c(uni_lemma, definition),
                   names_to = "x", values_to = "option") |>
      filter(!is.na(option)) |>
      dplyr::select(-x) |>
      mutate(language = lang)
  } else {
    special_case_map <- tibble(language = character(), uni_lemma = character(),
                               definition = character(), option = character())
  }
  return(special_case_map)
}

build_options <- function(language, word, special_cases) {
  opts <- c(word, special_cases)
  opts <- c(opts, word |> str_split("[,/]") |> unlist()) # "foo, bar", "foo/bar"
  opts <- c(opts, map(transforms, \(t) t(opts)))
  opts <- opts |> unlist() |> unique() |> str_trim()
  opts <- c(opts, stem(opts, language))
  return(unique(opts))
}
transforms <- list(
  \(s) str_replace_all(s, "(.*) \\(.*\\)", "\\1"), # foo (bar) -> foo
  \(s) str_replace_all(s, " ", "_"), # foo bar -> foo_bar
  \(s) str_replace_all(s, " ", "+"), # foo bar -> foo+bar
  \(s) str_replace_all(s, "(.+) \\1", "\\1") # (foo) bar -> bar
)

build_definition_map <- function(uni_lemmas) {
  special_case_map <- unique(uni_lemmas$language) |>
    map_df(build_special_case_map) |>
    group_by(language, uni_lemma, definition) |>
    summarise(special_cases = list(option))
  uni_lemmas |>
    left_join(special_case_map) |>
    mutate(option = pmap(list(language, definition, special_cases),
                         build_options)) |>
    dplyr::select(language, definition, option) |>
    unnest(option) |>
    mutate(option = tolower(option))
}

build_uni_lemma_map <- function(uni_lemmas) {
  special_case_map <- unique(uni_lemmas$language) |>
    map_df(build_special_case_map) |>
    group_by(language, uni_lemma, definition) |>
    summarise(special_cases = list(option))
  uni_lemmas |>
    left_join(special_case_map) |>
    mutate(option = pmap(list(language, definition, special_cases),
                         build_options)) |>
    dplyr::select(language, uni_lemma, option) |>
    unnest(option) |>
    mutate(option = tolower(option))
}
```

```{r load-orig-data, echo=F, message=F, warning=F}
# ToDo: remove book-reading corpora from CHILDES data!
# CHILDES corpus (hapaxes already removed, but 6295 word_count==2)

definition_map <- build_definition_map(uni_lemmas)
uni_lemma_map <- build_uni_lemma_map(uni_lemmas)

child_speech <- readRDS(here("data/token_metrics_french_(french).rds")) %>%
  rename(word_count = count ) %>%
  filter(!word_count==1) %>%
  mutate(word_count_norm=word_count * (1e6 / sum(word_count))) %>%
  arrange(desc(word_count)) %>%
  dplyr::select(token, word_count, word_count_norm) %>%
  distinct() %>%
  mutate(rank = 1:n()) 
  
cdi_items <- unique(wb_data$uni_lemma)

child_speech_mapped <- child_speech |>
   dplyr::select(token) |>
   filter(!token=="")|>
    mutate(token_self = token,
           token_stemmed = stem(token, lang)) |>
    pivot_longer(c(token_self, token_stemmed), names_to = "src",
                 values_to = "option") |>
    filter(!is.na(option), option != "") |>
    dplyr::select(-src) |>
    distinct() |>
    inner_join(uni_lemma_map) |>
    dplyr::select(-option)|>
    distinct()|>
    filter(!is.na(uni_lemma)) |>
   left_join(aoas_unilemma) |>
   dplyr::select(token, measure, aoa, uni_lemma)

#child_speech_matched <-unique(list(child_speech_mapped$token))
  
 
child_speech <- child_speech |>
    mutate(on_cdi = ifelse(as.character(token) %in% child_speech_matched[[1]], 1, 0),
           source="child_speech") 

saveRDS(child_speech_mapped, "data/aoas_token_fr.rds")

##############################################
adult_speech <- readLines("data/fr_adult_speech/try1.txt")

```

```{r adult_speech, echo=F, message=F, warning=F}
dat <- map(adult_speech, function(x) {
  tibble(text = unlist(str_split(x, pattern = "\\n"))) 
})

adult_speech <- do.call(rbind.data.frame, dat) %>%
  separate_rows(text, sep = ' ') %>%
  group_by(word = tolower(text)) %>%
  summarise(word_count = n(),
      sum_count = sum(word_count))%>%
  mutate(word_count_norm=word_count * (1e6 / sum(word_count))) %>%
  arrange(desc(word_count_norm)) %>%
  filter(!word_count==1) %>%
  filter(!word=="") %>%
  mutate(rank = 1:n()) %>%
  dplyr::select(word, word_count, word_count_norm, rank) %>%
  rename(token=word) 

adult_speech_mapped <- adult_speech |>
   filter(!token=="")|>
    mutate(token_self = token,
           token_stemmed = stem(token, lang)) |>
    pivot_longer(c(token_self,  token_stemmed), names_to = "src",
                 values_to = "option") |>
    dplyr::select(-src) |>
    inner_join(uni_lemma_map) |>
    dplyr::select(-option)|>
    distinct()|>
    filter(!is.na(uni_lemma))

 adult_speech_matched <-unique(list(adult_speech_mapped$token))
 
 adult_speech <- adult_speech |>
    mutate(on_cdi = ifelse(as.character(token) %in% adult_speech_matched[[1]], 1, 0),
           source="adult_speech") 

######################################################
adult_book <- readLines(here("data/fr_adult_book/adult_books_voltaire.txt")) 
dat <- map(adult_book, function(x) {
  tibble(text = unlist(str_split(x, pattern = "\\n"))) 
})
adult_book <- do.call(rbind.data.frame, dat) %>%
  separate_rows(text, sep = ' ') %>%
  group_by(word = tolower(text)) %>%
  summarise(word_count = n(),
      sum_count = sum(word_count))%>%
  mutate(word_count_norm=word_count * (1e6 / sum(word_count))) %>%
  filter(!word_count==1) %>%
  arrange(desc(word_count_norm)) %>%
  mutate(rank = 1:n()) %>%
  dplyr::select(word, word_count, word_count_norm, rank) %>%
  rename(token=word) 

adult_book_mapped <- adult_book |>
   filter(!token=="")|>
    mutate(token_self = token,
           token_stemmed = stem(token, lang)) |>
    pivot_longer(c(token_self,  token_stemmed), names_to = "src",
                 values_to = "option") |>
    dplyr::select(-src) |>
    inner_join(uni_lemma_map) |>
    dplyr::select(-option)|>
    distinct()|>
    filter(!is.na(uni_lemma))

 adult_book_matched <-unique(list(adult_book_mapped$token))
  
 adult_book <- adult_book |>
    mutate(on_cdi = ifelse(as.character(token) %in% adult_book_matched[[1]], 1, 0),
           source="adult_book")
########################################################
 
```

 
 
```{r child_book, echo=F, message=F, warning=F}

child_books <- readLines(here("data/web_stories_french.txt"))
                        
dat <- map(child_books, function(x) {
  tibble(text = unlist(str_split(x, pattern = "\\n"))) 
})
child_book <- do.call(rbind.data.frame, dat) %>%
  separate_rows(text, sep = ' ') %>%
  group_by(word = tolower(text)) %>%
  summarise(word_count = n(),
      sum_count = sum(word_count))%>%
  mutate(word_count_norm=word_count * (1e6 / sum(word_count))) %>%
   filter(!word_count==1) %>%
  arrange(desc(word_count_norm)) %>%
  mutate(rank = 1:n()) %>%
  dplyr::select(word, word_count, word_count_norm, rank) %>%
  rename(token=word)                        
                      
child_book_mapped <- child_book |>
   filter(!token=="")|>
    mutate(token_self = token,
           token_stemmed = stem(token, lang)) |>
    pivot_longer(c(token_self,  token_stemmed), names_to = "src",
                 values_to = "option") |>
    dplyr::select(-src) |>
    left_join(uni_lemma_map) |>
    dplyr::select(-option)|>
    distinct()|>
    filter(!is.na(uni_lemma))

child_book_matched <-unique(list(child_book_mapped$token))
  
child_book <- child_book |>
    mutate(on_cdi = ifelse(as.character(token) %in% child_book_matched[[1]], 1, 0),
           source="child_book")

```

Our data sources:

- Adult speech: `r nrow(adult_speech)` types, `r sum(adult_speech$word_count)` tokens from the orpus (`r sum(adult_speech$on_cdi)` CDI words)
- Children speech: `r nrow(child_speech)` types, `r sum(child_speech$word_count)` tokens from the CHILDES corpus (`r sum(child_speech$on_cdi)` CDI words)
- Adult books: `r nrow(adult_book)` types, `r sum(adult_book$word_count)` tokens from the books corpus
- Children's books: `r nrow(child_book)` types, `r sum(child_book$word_count)` tokens from the CHILDES corpus (`r sum(child_book$on_cdi)` CDI words)


## Normalize Word Frequencies

We will calculate keyness scores for each word, i.e. the ratio of normalized frequency in focus corpus to normalized frequency in a reference corpus.
For now, we will use the subset of words that are found in all four corpora (N=4229), but we may consider following Dawson et al. (2021) and adding a constant (e.g., 10) to all normalized frequencies in every corpus in order to not eliminate the bulk of words that do not appear in the smaller corpora (which are the child-directed corpora).
<!-- "Given the problem of calculating ratios for words occurring in the focus corpus, but not at all in the reference corpus, we added a constant of 10 to all normalised frequencies before calculating keyness. We selected this value as the constant because it focuses the keyword analysis on the lower end of the frequency spectrum (Kilgarriff, 2009), which we considered to be important when identifying the words that children were unlikely to encounter in everyday conversation, but which they would experience through regular exposure to book language." --> 


### Child-directed Speech vs. Books

```{r keyness-childes-vs-montag, echo=F}
# CHILDES and Stories books
ch_freq_long <- rbind(child_speech, child_book) %>%
  dplyr::select(token, source, on_cdi, word_count_norm, word_count)  

# wide - no smoothing, only keep subset of words in all corpora
ch_freq <- ch_freq_long %>% dplyr::select(-word_count) %>%
  pivot_wider(names_from = source, values_from = word_count_norm) %>%
  filter(!is.na(`child_book`), !is.na(child_speech)) %>%
  mutate(ch_book_vs_speech = `child_book` / child_speech,
         prop_booky = `child_book` / (`child_book` + child_speech)) 

# Laplace smoothing, alpha=10, keep all words in any corpus
ch_freq_smooth <- ch_freq_long %>% 
  mutate(word_count_norm_smooth = word_count_norm + 10) %>%
  pivot_wider(id_cols = c(token, on_cdi), names_from = source, values_from = word_count_norm_smooth, values_fill=10) %>% 
  filter(!is.na(`child_book`), !is.na(child_speech)) %>%
  mutate(ch_book_vs_speech = `child_book` / child_speech,
         prop_booky = `child_book` / (`child_book` + child_speech))
```


### Most Child Booky Words

```{r}
#ch_freq %>% arrange(desc(ch_book_vs_speech)) %>% head(10) %>% kable(digits=2)
#ch_freq_smooth %>% arrange(desc(ch_book_vs_speech)) %>% head(10) %>% kable(digits=2)

p1 <- ch_freq %>% mutate(Word = ifelse(on_cdi==1, "CDI", "Non-CDI")) %>%
  ggplot(aes(x=child_speech, y=`child_book`, color=Word)) + 
  geom_point(alpha=.3) + theme_classic() + geom_smooth(method='lm') +
  scale_x_log10() + scale_y_log10() + ggtitle("Raw Frequencies (intersection)")

p2 <- ch_freq_smooth %>% mutate(Word = ifelse(on_cdi==1, "CDI", "Non-CDI")) %>%
  ggplot(aes(x=child_speech, y=`child_book`, color=Word)) + 
  geom_point(alpha=.3) + theme_classic() + geom_smooth(method='lm') +
  scale_x_log10() + scale_y_log10() + ggtitle("Smoothed Frequencies (union)")

ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
```


```{r}
cor(subset(ch_freq, on_cdi==1)$child_speech, subset(ch_freq, on_cdi==1)$`child_book`) # .62
cor(subset(ch_freq, on_cdi==0)$child_speech, subset(ch_freq, on_cdi==0)$`child_book`) # .44
```

### Which CDI words are more booky/speechy?

```{r, fig.width=10, fig.height=5}
p1 <- ch_freq_smooth %>% filter(on_cdi==1) %>%
  ggplot(aes(x=child_speech, y=`child_book`)) + 
  geom_point(alpha=.3) + theme_classic() + 
  scale_x_log10() + scale_y_log10() +
  geom_text_repel(aes(label=token)) +
  geom_abline(intercept = 0, slope = 1, linetype="dashed") +
  ggtitle("CHILDES vs. Stories corpus")
p1
```



```{r}
library(spacyr)
library(udpipe)

ud_model <- udpipe_download_model(language = "french")
ud_model <- udpipe_load_model(ud_model$file_model)

child_speech_mapped <- child_speech_mapped %>% filter(measure=="produces")

mappings <- child_book_mapped %>% 
  dplyr::select(token, uni_lemma) %>% 
  rbind(child_speech_mapped %>% dplyr::select(token, uni_lemma)) %>% 
  distinct() %>% 
  full_join(uni_lemmas) %>%
  dplyr::select(token, lexical_class, uni_lemma) %>% 
  distinct()

ch_freq_ <- ch_freq %>% left_join(mappings)
x_<-((ch_freq_ %>% filter(is.na(lexical_class))))

x__ <- udpipe_annotate(ud_model, x = x_$token, doc_id = x_$token)
x <- as.data.frame(x___) %>%
  mutate(lexical_class1=ifelse(upos=="VERB", "verbs", upos),
         lexical_class1=ifelse(upos=="NOUN", "nouns", lexical_class1),
         lexical_class1=ifelse(upos=="AUX", "verbs", lexical_class1),
         lexical_class1=ifelse(upos=="ADJ", "adjectives", lexical_class1),
         lexical_class1=ifelse(upos=="ADP", "function_words", lexical_class1),
         lexical_class1=ifelse(upos=="DET", "function_words", lexical_class1),
         lexical_class1=ifelse(upos=="CCONJ", "function_words", lexical_class1),
          lexical_class1=ifelse(upos=="INTJ", "function_words", lexical_class1),
          lexical_class1=ifelse(upos=="ADV", "adverbs", lexical_class1),
          lexical_class1=ifelse(upos=="NUM", "function_words", lexical_class1),
          lexical_class1=ifelse(upos=="PROPN", "nouns", lexical_class1),
          lexical_class1=ifelse(upos=="PART", "function_words", lexical_class1),
          lexical_class1=ifelse(upos=="CCONJ", "function_words", lexical_class1),
          lexical_class1=ifelse(upos=="PRON", "function_words", lexical_class1),
          lexical_class1=ifelse(upos=="SCONJ", "function_words", lexical_class1)) %>%
        dplyr::select(doc_id, lexical_class1) %>%
        filter(!is.na(lexical_class1)) %>%
        rename("token"="doc_id")


ch_freq_new <- ch_freq_ %>% left_join(x) %>% 
  mutate(lexical_class=ifelse(is.na(lexical_class), lexical_class1, lexical_class )) %>%
  dplyr::select(-uni_lemma, -lexical_class1) %>%
  distinct() 

ch_freq_smooth_ <- ch_freq_smooth %>% left_join(mappings)
ch_freq_smooth_new<- ch_freq_ %>% left_join(x) %>% 
  dplyr::select(-uni_lemma) %>%
  distinct() %>%
  mutate(lexical_class=ifelse(is.na(lexical_class), lexical_class1, lexical_class )) %>%
  dplyr::select(-lexical_class1) %>%
  distinct() 

# holds even if we filter out many low frequency words
ch_key <- ch_freq_new %>% filter(child_speech>1, `child_book`>1) %>%
  group_by(on_cdi, lexical_class) %>%
  tidyboot_mean(ch_book_vs_speech)

ch_key_smooth <- ch_freq_smooth_new %>% 
  group_by(on_cdi, lexical_class) %>%
  tidyboot_mean(ch_book_vs_speech)

p1 <- ch_key %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean, color=lexical_class)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper), position = position_jitter(w=0.1)) +
  theme_classic() + ylab("Children's Book Keyness") + xlab("")

p2 <- ch_key_smooth %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean, color=lexical_class)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper), position = position_jitter(w=0.1)) +
  theme_classic() + ylab("Children's Book Keyness") + xlab("")

ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)



ch_freq_smooth1<- ch_freq_smooth_new |>
  group_by(token, prop_booky, on_cdi, child_speech, child_book,ch_book_vs_speech) |>
    summarise(
      lexical_category = list(lexical_class)) |>
  distinct()



save(ch_freq, ch_freq_smooth1, file="data/merged_word_freqs_fr.Rdata")


```

```{r}
ch_booky <- ch_freq_new %>% group_by(on_cdi, lexical_class) %>%
  tidyboot_mean(prop_booky)

ch_booky_smooth <- ch_freq_smooth_new %>% group_by(on_cdi, lexical_class) %>%
  tidyboot_mean(prop_booky)

p1 <- ch_booky %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean, color=lexical_class)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper), position = position_jitter(w=0.1)) +
  theme_classic() + ylab("Proportion of Book Occurrences") + xlab("")

p2 <- ch_booky_smooth %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean, color=lexical_class)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper), position = position_jitter(w=0.1)) +
  theme_classic() + ylab("Proportion of Book Occurrences") + xlab("")

ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
```

## Predicting AoA

Which corpus best predicts words' AoA?
Which corpora contribute unique variance to predicting AoA?
(Does the book corpus interact with SES, since we expect high-SES parents read more to their children?)

```{r}
dd <- ch_freq_smooth %>% filter(on_cdi==1) %>% 
  dplyr::select(-ch_book_vs_speech) %>% left_join(mappings) %>% left_join(aoas_unilemma)
  
dd_produces <- dd %>% filter(measure=="produces")
summary(lm(aoa ~ prop_booky, data=dd_produces)) # r^2 = .05; more booky = harder (significant)

dd_understands <- dd %>% filter(measure=="understands")
summary(lm(aoa ~ prop_booky, data=dd_understands)) # r^2 = .04; more booky = harder (significant)

# with the 2 sources, only books are significant
summary(lm(aoa ~ child_book + child_speech , data=dd_produces)) 
```


## Predict Booky Vocabulary per child by Mother Education

(also try ses_group)

```{r}
# let's take the 200 bookiest CDI items and look at relation of subscore to mom_ed
booky_items <- dd %>% arrange(desc(prop_booky)) %>% head(200)

```


## Also try same regressions controlling for Google books frequency (reference corpus) 


### Comparing to Adult Speech

For our reference corpus, we will use adult speech (movie subtitles), as this is the target language distribution that children will eventually learn.
(Although we could use child-directed speech, as that is what is given to children, or Google book frequency, which could be considered the epitome of an 'educated' distribution.)

```{r keyness-subtlex, echo=F, eval=F}
#all_freq_long <- rbind(child_speech, adult_speech, child_books, adult_books) %>%
#  dplyr::select(word, source, on_cdi, word_count_norm) #%>%
#  filter(!is.element(word, c("d","m","s","t", "xxx"))) 

# wide - no smoothing, only keep subset of words in all corpora
#all_freq <- all_freq_long %>%
#  pivot_wider(names_from = source, values_from = word_count_norm) %>%
#  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(SUBTLEX), !is.na(`Adult Books`)) #%>%
#  mutate(child_vs_adult_speech = CHILDES / SUBTLEX, 
#         child_book_vs_adult_speech = `Children's Books` / SUBTLEX,
#         adult_books_vs_speech = `Adult Books` / SUBTLEX)
         #ch_book_ad_book_ratio = `Children's Books` / `Adult Books`,
         #ch_book_ad_book_ratio = `Children's Books` / CHILDES) # are children's books like adult books, or like children's speech?

# Laplace smoothing, alpha=1, keep all 123060 words in any corpus
#all_freq_smooth <- all_freq_long %>% 
#  mutate(word_count_norm_smooth = word_count_norm + 1) %>%
#  pivot_wider(id_cols = c(word, on_cdi), names_from = source, values_from = word_count_norm_smooth, values_fill=1) %>% 
#  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(SUBTLEX), !is.na(`Adult Books`)) #%>%
#  mutate(child_vs_adult_speech = CHILDES / SUBTLEX, 
#         child_book_vs_adult_speech = `Children's Books` / SUBTLEX,
#         adult_books_vs_speech = `Adult Books` / SUBTLEX)
```

Non-SUBTLEX adult speech (Charlesworth corpus):

```{r keyness-charlesworth, echo=F, eval=F}
#all_freq_long <- rbind(child_speech, adult_speech2, child_books, adult_books) %>%
#  select(word, source, on_cdi, word_count_norm) %>%
#  filter(!is.element(word, c("d","m","s","t", "xxx", "child's own name"))) 

# wide - no smoothing, only keep subset of 3977 words in all corpora
#all_freq <- all_freq_long %>%
#  pivot_wider(names_from = source, values_from = word_count_norm) %>%
#  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(speech), !is.na(`Adult Books`)) #%>%
#  mutate(child_vs_adult_speech = CHILDES / speech, 
#         child_book_vs_adult_speech = `Children's Books` / speech,
#         adult_books_vs_speech = `Adult Books` / speech)

# Laplace smoothing, alpha=10, keep all 115597 words in any corpus
#all_freq_smooth <- all_freq_long %>% 
#  mutate(word_count_norm_smooth = word_count_norm + 10) %>%
#  pivot_wider(id_cols = c(word, on_cdi), names_from = source, values_from = #word_count_norm_smooth, values_fill=10) %>% 
#  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(speech), !is.na(`Adult Books`)) #%>%
#  mutate(child_vs_adult_speech = CHILDES / speech, 
#         child_book_vs_adult_speech = `Children's Books` / speech,
#         adult_books_vs_speech = `Adult Books` / speech)
```

## Child-directed speech vs. Adult speech

We first examine the keyness of words in child-directed speech vs. that in adult speech.
Here are the 10 words most over-represented in child-directed speech compared to adult movies:

```{r, echo=F, eval=F}
# top 10
#all_freq %>% arrange(desc(child_vs_adult_speech)) %>% head(10) %>% kable(digits=2)
#all_freq_smooth %>% arrange(desc(child_vs_adult_speech)) %>% head(10) %>% kable(digits=2)
```


Here are the 10 words most under-represented in CHILDES, compared to adult movies:

```{r, echo=F, eval=F}
#all_freq %>% arrange(desc(child_vs_adult_speech)) %>% tail(10) %>% kable(digits=2)
#all_freq_smooth %>% arrange(desc(child_vs_adult_speech)) %>% tail(10) %>% kable(digits=2)
```


Below we show the average keyness of child-directed speech and children's books for CDI vs. non-CDI words, using adult speech as the reference corpus.
This is based on the words common to all corpora.

```{r, keyness-cdi-confint, echo=F, eval=F, fig.width=8, fig.height=3.5}
#ch_book <- all_freq %>% group_by(on_cdi) %>%
#  tidyboot_mean(child_book_vs_adult_speech)

#ch_speech <- all_freq %>% group_by(on_cdi) %>%
#  tidyboot_mean(child_vs_adult_speech)

#ad_speech <- all_freq %>% group_by(on_cdi) %>%
#  tidyboot_mean(adult_books_vs_speech)

#p1 <- ch_book %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
#  ggplot(aes(x=CDI, y=mean)) + 
#  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
#  theme_classic() + ylab("Children's Books Keyness") #+ ylim(0,20)

#p2 <- ch_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
#  ggplot(aes(x=CDI, y=mean)) + 
#  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
#  theme_classic() + ylab("Child-directed Speech Keyness") #+ ylim(0,6)

#p3 <- ad_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
#  ggplot(aes(x=CDI, y=mean)) + 
#  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
#  theme_classic() + ylab("Adult Books Keyness") + ylim(0,5)

#ggpubr::ggarrange(p1, p2, p3, nrow=1)
```

Now we do the same for the union of all words across the corpora (Laplace-smoothed).

```{r, keyness-cdi-confint-smooth, echo=F, eval=F, fig.width=8, fig.height=3.5}
#ch_book <- all_freq_smooth %>% group_by(on_cdi) %>%
#  tidyboot_mean(child_book_vs_adult_speech)

#ch_speech <- all_freq_smooth %>% group_by(on_cdi) %>%
#  tidyboot_mean(child_vs_adult_speech)

#ad_speech <- all_freq_smooth %>% group_by(on_cdi) %>%
#  tidyboot_mean(adult_books_vs_speech)

#p1 <- ch_book %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
#  ggplot(aes(x=CDI, y=mean)) + 
#  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
#  theme_classic() + ylab("Children's Books Keyness") #+ ylim(0,20)

#p2 <- ch_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
#  ggplot(aes(x=CDI, y=mean)) + 
#  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
#  theme_classic() + ylab("Child-directed Speech Keyness") #+ ylim(0,6)

#p3 <- ad_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
#  ggplot(aes(x=CDI, y=mean)) + 
#  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
#  theme_classic() + ylab("Adult Books Keyness") #+ ylim(0,5)

#ggpubr::ggarrange(p1, p2, p3, nrow=1)
```


## Other Ideas

- Does the mean IRT difficulty of CDI/non-CDI words systematically vary with the source?
- Use adult books as reference corpus for keyness metric (instad of subtitles)
