---
title: "Where do CDI words come from?"
author: "George & Georgia"
date: "9/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(here)
require(ggrepel)
require(kableExtra)
require(tidyboot)
require(readr)
require(tokenizers)
```


## Goal

Investigate whether inclusion on the CDI is more predicted by frequency in adult- or children-oriented sources, including books, television, and speech.
To start, we will look at American English, before extending to British English and French.
We will begin with unlemmatized corpora, and disregard part-of-speech classification.

```{r load-data, echo=F, eval=F}
process_text <- function(path, source_name) {
  words = tokenize_words(read_file(path))
  tab <- table(words[[1]])
  wf <- data_frame(word = names(tab), word_count = as.numeric(tab)) %>%
    mutate(source = source_name,
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count)) %>%
    mutate(word = ifelse(word=="i", "I", ifelse(word=="i'll", "I'll", word))) %>%
    arrange(desc(word_count_norm)) %>%
    mutate(rank = 1:n())
  print(paste0("loaded ", nrow(wf), " word types (", sum(wf$word_count)," tokens)"))
  return(wf)
}

data_dir = "data/Charlesworth-Clean-data/"
adult_dat <- process_text(here(paste0(data_dir, "Adult_Books/gutenberg_corpus.txt")), "books")
adult_dat <- adult_dat %>% bind_rows(process_text(here(paste0(data_dir, "Adult_Speech/adult_speech_corpus.txt")), "speech")) # or lemmatized_adult_speech_corpus.txt
# loaded 27536 word types (3104328 tokens)
adult_dat <- adult_dat %>% bind_rows(process_text(here(paste0(data_dir, "Adult_TV/pbs_adults_corpus.txt")), "tv1"))
# loaded 45351 word types (4175570 tokens)
adult_dat <- adult_dat %>% bind_rows(process_text(here(paste0(data_dir, "Adult_TV/simply_scripts_corpus.txt")), "tv2"))
# loaded 103079 word types (2056384 tokens)

child_dat <- bind_rows(
  process_text(here(paste0(data_dir, "Child_Books/unlemmatized_child_books.txt")), "books"),
  process_text(here(paste0(data_dir, "Child_TV/childrens_tv_combined_corpus.txt")), "tv"),
  process_text(here(paste0(data_dir, "CHILDES clean text/corpus_parents.txt")), "speech")
  )
# loaded 42652 word types (4730867 tokens)
# loaded 84341 word types (6759928 tokens)
# loaded 38770 word types (5495648 tokens)

save(adult_dat, child_dat, file="data/Charlesworth-unlemmatized-counts.Rdata")
```

```{r load-orig-data, echo=F, message=F, warning=F}
# ToDo: remove book-reading corpora from CHILDES data!
# CHILDES corpus (hapaxes already removed, but 6295 word_count==2)
child_speech <- read_csv(here("data/childes_english_word_freq_cleaned_noHapaxes.csv")) %>% 
  select(-X1) %>%
  mutate(source = "CHILDES") %>% 
  arrange(desc(word_count)) %>%
  mutate(rank = 1:n())

cdi_voc = subset(child_speech, on_cdi==1)$word # 657 / 680 -- should check other 23 words

# SUBTLEX-US subtitle word frequencies (adult speech standard), min freq = 2
adult_speech <- read_csv(here("data/SUBTLEX-US.csv")) %>% # 50.3 million words
  rename(word_count_norm = SUBTLWF, # frequency per million words
         word_count = SLUSfreq) %>%
  mutate(word = tolower(word)) %>%
  group_by(word) %>%
  summarise(word_count = sum(word_count)) %>%
  mutate(source = "SUBTLEX",
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count)) %>%
  mutate(word = ifelse(word=="i", "I", word)) %>%
  arrange(desc(word_count_norm)) %>%
  mutate(rank = 1:n()) %>%
  select(word, word_count, word_count_norm, prob, source, rank) %>%
  mutate(on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) # 610 CDI words

# SUBTLEX is missing all of the apostrophized words...let's use the Charlesworth corpus instead

# Google book frequencies (743.8 billion words) min freq = 100005
adult_books <- read.csv(here("data/google-books-common-words.txt"), sep='\t') %>%
  mutate(word = tolower(word),
         word = ifelse(word=="i", "I", word),
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count),
         source = "Adult Books") %>%
  arrange(desc(word_count)) %>%
  mutate(rank = 1:n(),
         on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) # 643

# min freq = 1 (2548, but mostly real words)
child_books <- read.csv(here("data/Montag-book-corpus/100out.txt"), sep=' ') %>% 
  mutate(word = ifelse(word=="i", "I", word),
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count),
         source = "Children's Books"
  ) %>%
  arrange(desc(word_count)) %>%
  mutate(rank = 1:n(),
         on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) 
```

Our data sources:

- Adult speech: `r nrow(adult_speech)` types, `r sum(adult_speech$word_count)` tokens from the CHILDES corpus (`r sum(adult_speech$on_cdi)` CDI words)
- Children speech: `r nrow(child_speech)` types, `r sum(child_speech$word_count)` tokens from the CHILDES corpus (`r sum(child_speech$on_cdi)` CDI words)
- Adult books: `r nrow(adult_books)` types, `r sum(adult_books$word_count)` tokens from the Google books corpus
- Children's books: `r nrow(child_books)` types, `r sum(child_books$word_count)` tokens from the CHILDES corpus (`r sum(child_books$on_cdi)` CDI words)


## Normalize Word Frequencies

We will calculate keyness scores for each word, i.e. the ratio of normalized frequency in focus corpus to normalized frequency in a reference corpus.
For now, we will use the subset of words that are found in all four corpora (N=4229), but we may consider following Dawson et al. (2021) and adding a constant (e.g., 10) to all normalized frequencies in every corpus in order to not eliminate the bulk of words that do not appear in the smaller corpora (which are the child-directed corpora).
<!-- "Given the problem of calculating ratios for words occurring in the focus corpus, but not at all in the reference corpus, we added a constant of 10 to all normalised frequencies before calculating keyness. We selected this value as the constant because it focuses the keyword analysis on the lower end of the frequency spectrum (Kilgarriff, 2009), which we considered to be important when identifying the words that children were unlikely to encounter in everyday conversation, but which they would experience through regular exposure to book language." --> 

For our reference corpus, we will use adult speech (movie subtitles), as this is the target language distribution that children will eventually learn.
(Although we could use child-directed speech, as that is what is given to children, or Google book frequency, which could be considered the epitome of an 'educated' distribution.)

```{r keyness, echo=F}
all_freq_long <- rbind(child_speech, adult_speech, child_books, adult_books) %>%
  select(word, source, on_cdi, word_count_norm) %>%
  filter(!is.element(word, c("d","m","s","t", "xxx"))) 

# wide - no smoothing, only keep subset of words in all corpora
all_freq <- all_freq_long %>%
  pivot_wider(names_from = source, values_from = word_count_norm) %>%
  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(SUBTLEX), !is.na(`Adult Books`)) %>%
  mutate(child_vs_adult_speech = CHILDES / SUBTLEX, 
         child_book_vs_adult_speech = `Children's Books` / SUBTLEX,
         adult_books_vs_speech = `Adult Books` / SUBTLEX)
         #ch_book_ad_book_ratio = `Children's Books` / `Adult Books`,
         #ch_book_ad_book_ratio = `Children's Books` / CHILDES) # are children's books like adult books, or like children's speech?

# Laplace smoothing, alpha=1, keep all 123060 words in any corpus
all_freq_smooth <- all_freq_long %>% 
  mutate(word_count_norm_smooth = word_count_norm + 1) %>%
  pivot_wider(id_cols = c(word, on_cdi), names_from = source, values_from = word_count_norm_smooth, values_fill=1) %>% 
  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(SUBTLEX), !is.na(`Adult Books`)) %>%
  mutate(child_vs_adult_speech = CHILDES / SUBTLEX, 
         child_book_vs_adult_speech = `Children's Books` / SUBTLEX,
         adult_books_vs_speech = `Adult Books` / SUBTLEX)
```

## Child-directed speech vs. Adult speech

We first examine the keyness of words in child-directed speech vs. that in adult speech.
Here are the 10 words most over-represented in child-directed speech compared to adult movies:

```{r, echo=F}
# top 10
all_freq %>% arrange(desc(child_vs_adult_speech)) %>% head(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(child_vs_adult_speech)) %>% head(10) %>% kable(digits=2)
```


Here are the 10 words most under-represented in CHILDES, compared to adult movies:

```{r, echo=F}
all_freq %>% arrange(desc(child_vs_adult_speech)) %>% tail(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(child_vs_adult_speech)) %>% tail(10) %>% kable(digits=2)
```


## Children's books vs. adult speech

Here are the 10 words most over-represented in children's books compared to adult speech:

```{r, echo=F}
all_freq %>% arrange(desc(child_book_vs_adult_speech)) %>% head(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(child_book_vs_adult_speech)) %>% head(10) %>% kable(digits=2)
```


Here are the 10 words most under-represented in CHILDES compared to adult speech:

```{r, echo=F}
all_freq %>% arrange(desc(child_book_vs_adult_speech)) %>% tail(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(child_book_vs_adult_speech)) %>% tail(10) %>% kable(digits=2)
```

## Adult books vs. adult speech

For comparison, here are the 10 words most over-represented in adult books compared to adult speech:

```{r, echo=F}
all_freq %>% arrange(desc(adult_books_vs_speech)) %>% head(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(adult_books_vs_speech)) %>% head(10) %>% kable(digits=2)
```


and the 10 words most under-represented in adult books compared to adult speech:

```{r, echo=F}
all_freq %>% arrange(desc(adult_books_vs_speech)) %>% tail(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(adult_books_vs_speech)) %>% tail(10) %>% kable(digits=2)
```


# Keyness of CDI words vs. non-CDI words 

For just the `r nrow(all_freq)` words that occur in all four corpora:

```{r keyness-cdi-mean, eval=F, echo=F}
all_freq %>% group_by(on_cdi) %>%
  summarise(child_book_vs_adult_speech = mean(child_book_vs_adult_speech),
            child_vs_adult_speech = mean(child_vs_adult_speech),
            adult_books_vs_speech = mean(adult_books_vs_speech),
            n=n()) %>% kable(digits=2)
```

Now for the `r nrow(all_freq_smooth)` words appearing in any of the corpora, with Laplace-smoothed normalized frequencies:

```{r keyness-cdi-mean-smooth, eval=F, echo=F}
all_freq_smooth %>% group_by(on_cdi) %>%
  summarise(child_book_vs_adult_speech = mean(child_book_vs_adult_speech),
            child_vs_adult_speech = mean(child_vs_adult_speech),
            adult_books_vs_speech = mean(adult_books_vs_speech),
            n=n()) %>% kable(digits=2)
```

Below we show the average keyness of child-directed speech and children's books for CDI vs. non-CDI words, using adult speech as the reference corpus.
This is based on the words common to all corpora.

```{r, keyness-cdi-confint, echo=F, fig.width=8, fig.height=3.5}
ch_book <- all_freq %>% group_by(on_cdi) %>%
  tidyboot_mean(child_book_vs_adult_speech)

ch_speech <- all_freq %>% group_by(on_cdi) %>%
  tidyboot_mean(child_vs_adult_speech)

ad_speech <- all_freq %>% group_by(on_cdi) %>%
  tidyboot_mean(adult_books_vs_speech)

p1 <- ch_book %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Children's Books Keyness") + ylim(0,20)

p2 <- ch_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Child-directed Speech Keyness") + ylim(0,6)

p3 <- ad_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Adult Books Keyness") + ylim(0,5)

ggpubr::ggarrange(p1, p2, p3, nrow=1)
```

Now we do the same for the union of all words across the corpora (Laplace-smoothed).

```{r, keyness-cdi-confint-smooth, echo=F, fig.width=8, fig.height=3.5}
ch_book <- all_freq_smooth %>% group_by(on_cdi) %>%
  tidyboot_mean(child_book_vs_adult_speech)

ch_speech <- all_freq_smooth %>% group_by(on_cdi) %>%
  tidyboot_mean(child_vs_adult_speech)

ad_speech <- all_freq_smooth %>% group_by(on_cdi) %>%
  tidyboot_mean(adult_books_vs_speech)

p1 <- ch_book %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Children's Books Keyness") + ylim(0,20)

p2 <- ch_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Child-directed Speech Keyness") + ylim(0,6)

p3 <- ad_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Adult Books Keyness") + ylim(0,5)

ggpubr::ggarrange(p1, p2, p3, nrow=1)
```

## Predicting AoA

Which corpus best predicts words' AoA?
Which corpora contribute unique variance to predicting AoA?
(Does the book corpus interact with SES, since we expect high-SES parents read more to their children?)

```{r}
load("data/en_ws_production.Rdata")
```


## Other Ideas

- Does the mean IRT difficulty of CDI/non-CDI words systematically vary with the source?
- Use adult books as reference corpus for keyness metric (instad of subtitles)
