---
title: "Where do CDI words come from?"
author: "George & Georgia"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(here)
require(ggrepel)
require(kableExtra)
require(tidyboot)
require(readr)
require(tokenizers)
```


## Goal

Can we identify words on the CDI that are more bookish, speechy, or from TV? (Controlling for difficulty, as more bookish words are probably more difficult)

Using this distributional source information, can we find features of children (e.g., mother's education) that relate to knowledge of subsets of words (e.g. bookish words)?

To start, we will look at American English, before extending to British English and French.
We will begin with unlemmatized corpora, and disregard part-of-speech classification.

```{r load-data, echo=F, eval=F}
process_text <- function(path, source_name) {
  words = tokenize_words(read_file(path))
  tab <- table(words[[1]])
  wf <- data_frame(word = names(tab), word_count = as.numeric(tab)) %>%
    mutate(source = source_name,
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count)) %>%
    mutate(word = ifelse(word=="i", "I", ifelse(word=="i'll", "I'll", word))) %>%
    arrange(desc(word_count_norm)) %>%
    mutate(rank = 1:n())
  print(paste0("loaded ", nrow(wf), " word types (", sum(wf$word_count)," tokens)"))
  return(wf)
}

data_dir = "data/Charlesworth-Clean-data/"
adult_dat <- bind_rows(process_text(here(paste0(data_dir, "Adult_Books/gutenberg_corpus.txt")), "books"),
                       process_text(here(paste0(data_dir, "Adult_Speech/adult_speech_corpus.txt")), "speech")) 
# or lemmatized_adult_speech_corpus.txt
# loaded 827414 word types (35143617 tokens)
# loaded 27536 word types (3104328 tokens)


# combine the TV corpora
tv1 <- process_text(here(paste0(data_dir, "Adult_TV/pbs_adults_corpus.txt")), "tv1")
# loaded 45351 word types (4175570 tokens)
tv2 <- process_text(here(paste0(data_dir, "Adult_TV/simply_scripts_corpus.txt")), "tv2")
# loaded 103079 word types (2056384 tokens)
#tv1 %>% select(word, word_count) 

adult_tv <- full_join(tv1 %>% select(word, word_count), 
                      tv2 %>% select(word, word_count), by="word") %>%
  mutate(word_count.x = replace_na(word_count.x, 0),
         word_count.y = replace_na(word_count.y, 0),
         word_count = word_count.x + word_count.y) %>%
  select(word, word_count) %>%
  filter(word_count>1) %>% # hapaxes are mostly junk--phrases with spaces/punctuation removed
  mutate(source = "TV",
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count)) %>%
  mutate(word = ifelse(word=="i", "I", ifelse(word=="i'll", "I'll", word))) %>% # I'd I've..
  arrange(desc(word_count_norm)) %>%
  mutate(rank = 1:n())

adult_dat = bind_rows(adult_dat, adult_tv)

child_dat <- bind_rows(
  process_text(here(paste0(data_dir, "Child_Books/unlemmatized_child_books.txt")), "books"),
  process_text(here(paste0(data_dir, "Child_TV/childrens_tv_combined_corpus.txt")), "tv"),
  process_text(here(paste0(data_dir, "CHILDES clean text/corpus_parents.txt")), "speech")
  )
# loaded 42652 word types (4730867 tokens)
# loaded 84341 word types (6759928 tokens)
# loaded 38770 word types (5495648 tokens)


save(adult_dat, child_dat, file="data/Charlesworth-unlemmatized-counts.Rdata")
```

```{r load-orig-data, echo=F, message=F, warning=F}
# ToDo: remove book-reading corpora from CHILDES data!
# CHILDES corpus (hapaxes already removed, but 6295 word_count==2)
child_speech <- read_csv(here("data/childes_english_word_freq_cleaned_noHapaxes.csv")) %>% 
  select(-X1) %>%
  mutate(source = "CHILDES") %>%
#         word = tolower(word)) %>% 
#  mutate(word = ifelse(word=="i", "I", ifelse(word=="i'll", "I'll", word))) %>%
  arrange(desc(word_count)) %>%
  mutate(rank = 1:n())

#load("data/en_ws_production.Rdata")
#cdi_items = unique(d_en_ws$definition)

cdi_voc = subset(child_speech, on_cdi==1)$word # 657 / 680 -- should check other 23 words

# SUBTLEX-US subtitle word frequencies (adult speech standard), min freq = 2
adult_speech <- read_csv(here("data/SUBTLEX-US.csv")) %>% # 50.3 million words
  rename(word_count_norm = SUBTLWF, # frequency per million words
         word_count = SLUSfreq) %>%
  mutate(word = tolower(word)) %>%
  group_by(word) %>%
  summarise(word_count = sum(word_count)) %>%
  mutate(source = "SUBTLEX",
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count)) %>%
  mutate(word = ifelse(word=="i", "I", word)) %>%
  arrange(desc(word_count_norm)) %>%
  mutate(rank = 1:n()) %>%
  select(word, word_count, word_count_norm, prob, source, rank) %>%
  mutate(on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) # 610 CDI words

# SUBTLEX is missing all of the apostrophized words...let's use the Charlesworth corpus instead
load("data/Charlesworth-unlemmatized-counts.Rdata") 

adult_dat <- adult_dat %>% 
  mutate(on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) # 
table(adult_dat$on_cdi, adult_dat$source) 
# 638 CDI words in books, 618 in speech, 636 on TV

child_dat <- child_dat %>% 
  mutate(on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) 
table(child_dat$on_cdi, child_dat$source)
# 596 in books, 656 in speech, 652 on TV

# Google book frequencies (743.8 billion words) min freq = 100005
adult_books <- read.csv(here("data/google-books-common-words.txt"), sep='\t') %>%
  mutate(word = tolower(word),
         word = ifelse(word=="i", "I", word),
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count),
         source = "Adult Books") %>%
  arrange(desc(word_count)) %>%
  mutate(rank = 1:n(),
         on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) # 643

# min freq = 1 (2548, but mostly real words)
child_books <- read.csv(here("data/Montag-book-corpus/100out.txt"), sep=' ') %>% 
  mutate(word = ifelse(word=="i", "I", word),
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count),
         source = "Children's Books"
  ) %>%
  arrange(desc(word_count)) %>%
  mutate(rank = 1:n(),
         on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) 
```

Our data sources:

- Adult speech: `r nrow(adult_speech)` types, `r sum(adult_speech$word_count)` tokens from the SUBTLEX corpus (`r sum(adult_speech$on_cdi)` CDI words)
- Children speech: `r nrow(child_speech)` types, `r sum(child_speech$word_count)` tokens from the CHILDES corpus (`r sum(child_speech$on_cdi)` CDI words)
- Adult books: `r nrow(adult_books)` types, `r sum(adult_books$word_count)` tokens from the Google books corpus
- Children's books: `r nrow(child_books)` types, `r sum(child_books$word_count)` tokens from the CHILDES corpus (`r sum(child_books$on_cdi)` CDI words)


## Normalize Word Frequencies

We will calculate keyness scores for each word, i.e. the ratio of normalized frequency in focus corpus to normalized frequency in a reference corpus.
For now, we will use the subset of words that are found in all four corpora (N=4229), but we may consider following Dawson et al. (2021) and adding a constant (e.g., 10) to all normalized frequencies in every corpus in order to not eliminate the bulk of words that do not appear in the smaller corpora (which are the child-directed corpora).
<!-- "Given the problem of calculating ratios for words occurring in the focus corpus, but not at all in the reference corpus, we added a constant of 10 to all normalised frequencies before calculating keyness. We selected this value as the constant because it focuses the keyword analysis on the lower end of the frequency spectrum (Kilgarriff, 2009), which we considered to be important when identifying the words that children were unlikely to encounter in everyday conversation, but which they would experience through regular exposure to book language." --> 


### Child-directed Speech vs. Books

```{r keyness-childes-vs-montag, echo=F, eval=F}
# CHILDES and Montag books
ch_freq_long <- rbind(child_speech, child_books) %>%
  select(word, source, on_cdi, word_count_norm, word_count) %>%
  filter(!is.element(word, c("d","m","s","t", "xxx"))) 
# equivalent to child_dat, which is based on Charlesworth corpora

# wide - no smoothing, only keep subset of 4611 words in all corpora
ch_freq <- ch_freq_long %>% select(-word_count) %>%
  pivot_wider(names_from = source, values_from = word_count_norm) %>%
  filter(!is.na(`Children's Books`), !is.na(CHILDES)) %>%
  mutate(ch_book_vs_speech = `Children's Books` / CHILDES,
         prop_booky = `Children's Books` / (`Children's Books` + CHILDES)) 

# Laplace smoothing, alpha=10, keep all 123060 words in any corpus
ch_freq_smooth <- ch_freq_long %>% 
  mutate(word_count_norm_smooth = word_count_norm + 10) %>%
  pivot_wider(id_cols = c(word, on_cdi), names_from = source, values_from = word_count_norm_smooth, values_fill=10) %>% 
  filter(!is.na(`Children's Books`), !is.na(CHILDES)) %>%
  mutate(ch_book_vs_speech = `Children's Books` / CHILDES,
         prop_booky = `Children's Books` / (`Children's Books` + CHILDES))
```

```{r keyness-charlesworth-corpora, echo=F, eval=F}
# wide - no smoothing, only keep subset of 4611 words in all corpora
ch_freq_charles <- child_dat %>% select(-word_count) %>%
  pivot_wider(names_from = source, values_from = word_count_norm) %>%
  filter(!is.na(books), !is.na(speech)) %>%
  mutate(ch_book_vs_speech = books / speech,
         prop_booky = books / (books + speech)) 

# Laplace smoothing, alpha=10, keep all 124036 words in any corpus
ch_freq_smooth_charles <- child_dat %>% 
  mutate(word_count_norm_smooth = word_count_norm + 10) %>%
  pivot_wider(id_cols = c(word, on_cdi), names_from = source, values_from = word_count_norm_smooth, values_fill=10) %>% 
  filter(!is.na(books), !is.na(speech)) %>%
  mutate(ch_book_vs_speech = books / speech,
         prop_booky = books / (books + speech))
```

### Most Child Booky Words

```{r}
ch_freq %>% arrange(desc(ch_book_vs_speech)) %>% head(10) %>% kable(digits=2)
ch_freq_smooth %>% arrange(desc(ch_book_vs_speech)) %>% head(10) %>% kable(digits=2)

p1 <- ch_freq %>% mutate(Word = ifelse(on_cdi==1, "CDI", "Non-CDI")) %>%
  ggplot(aes(x=CHILDES, y=`Children's Books`, color=Word)) + 
  geom_point(alpha=.3) + theme_classic() + geom_smooth(method='lm') +
  scale_x_log10() + scale_y_log10() + ggtitle("Raw Frequencies (intersection)")

p2 <- ch_freq_smooth %>% mutate(Word = ifelse(on_cdi==1, "CDI", "Non-CDI")) %>%
  ggplot(aes(x=CHILDES, y=`Children's Books`, color=Word)) + 
  geom_point(alpha=.3) + theme_classic() + geom_smooth(method='lm') +
  scale_x_log10() + scale_y_log10() + ggtitle("Smoothed Frequencies (union)")

ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
```

## 

```{r}
cor(subset(ch_freq, on_cdi==1)$CHILDES, subset(ch_freq, on_cdi==1)$`Children's Books`) # .75
cor(subset(ch_freq, on_cdi==0)$CHILDES, subset(ch_freq, on_cdi==0)$`Children's Books`)
```

Of the words on the CDI, which are more booky/speechy?

```{r}
ch_freq_smooth %>% filter(on_cdi==1) %>%
  ggplot(aes(x=CHILDES, y=`Children's Books`)) + 
  geom_point(alpha=.3) + theme_classic() + 
  scale_x_log10() + scale_y_log10() +
  geom_text_repel(aes(label=word)) +
  geom_abline(intercept = 0, slope = 1, linetype="dashed")
  #geom_text(data=subset(ch_freq_smooth, on_cdi==1 & (wt > 4 | mpg > 25)), aes(label=name))

```

```{r}
ch_key <- ch_freq %>% group_by(on_cdi) %>%
  tidyboot_mean(ch_book_vs_speech)

ch_key_smooth <- ch_freq_smooth %>% group_by(on_cdi) %>%
  tidyboot_mean(ch_book_vs_speech)

p1 <- ch_key %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Children's Book Keyness") + xlab("")

p2 <- ch_key_smooth %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Children's Book Keyness") + xlab("")

ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
```

```{r}
ch_booky <- ch_freq %>% group_by(on_cdi) %>%
  tidyboot_mean(prop_booky)

ch_booky_smooth <- ch_freq_smooth %>% group_by(on_cdi) %>%
  tidyboot_mean(prop_booky)

p1 <- ch_booky %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Proportion of Book Occurrences") 

p2 <- ch_booky_smooth %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Proportion of Book Occurrences")

ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
```




### Reference Corpus: Adult Speech

For our reference corpus, we will use adult speech (movie subtitles), as this is the target language distribution that children will eventually learn.
(Although we could use child-directed speech, as that is what is given to children, or Google book frequency, which could be considered the epitome of an 'educated' distribution.)

```{r keyness-subtlex, echo=F, eval=F}
all_freq_long <- rbind(child_speech, adult_speech, child_books, adult_books) %>%
  select(word, source, on_cdi, word_count_norm) %>%
  filter(!is.element(word, c("d","m","s","t", "xxx"))) 

# wide - no smoothing, only keep subset of words in all corpora
all_freq <- all_freq_long %>%
  pivot_wider(names_from = source, values_from = word_count_norm) %>%
  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(SUBTLEX), !is.na(`Adult Books`)) %>%
  mutate(child_vs_adult_speech = CHILDES / SUBTLEX, 
         child_book_vs_adult_speech = `Children's Books` / SUBTLEX,
         adult_books_vs_speech = `Adult Books` / SUBTLEX)
         #ch_book_ad_book_ratio = `Children's Books` / `Adult Books`,
         #ch_book_ad_book_ratio = `Children's Books` / CHILDES) # are children's books like adult books, or like children's speech?

# Laplace smoothing, alpha=1, keep all 123060 words in any corpus
all_freq_smooth <- all_freq_long %>% 
  mutate(word_count_norm_smooth = word_count_norm + 1) %>%
  pivot_wider(id_cols = c(word, on_cdi), names_from = source, values_from = word_count_norm_smooth, values_fill=1) %>% 
  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(SUBTLEX), !is.na(`Adult Books`)) %>%
  mutate(child_vs_adult_speech = CHILDES / SUBTLEX, 
         child_book_vs_adult_speech = `Children's Books` / SUBTLEX,
         adult_books_vs_speech = `Adult Books` / SUBTLEX)
```

Non-SUBTLEX adult speech (Charlesworth corpus):

```{r keyness-charlesworth, echo=F}
all_freq_long <- rbind(child_speech, adult_speech2, child_books, adult_books) %>%
  select(word, source, on_cdi, word_count_norm) %>%
  filter(!is.element(word, c("d","m","s","t", "xxx", "child's own name"))) 

# wide - no smoothing, only keep subset of 3977 words in all corpora
all_freq <- all_freq_long %>%
  pivot_wider(names_from = source, values_from = word_count_norm) %>%
  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(speech), !is.na(`Adult Books`)) %>%
  mutate(child_vs_adult_speech = CHILDES / speech, 
         child_book_vs_adult_speech = `Children's Books` / speech,
         adult_books_vs_speech = `Adult Books` / speech)

# Laplace smoothing, alpha=10, keep all 115597 words in any corpus
all_freq_smooth <- all_freq_long %>% 
  mutate(word_count_norm_smooth = word_count_norm + 10) %>%
  pivot_wider(id_cols = c(word, on_cdi), names_from = source, values_from = word_count_norm_smooth, values_fill=10) %>% 
  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(speech), !is.na(`Adult Books`)) %>%
  mutate(child_vs_adult_speech = CHILDES / speech, 
         child_book_vs_adult_speech = `Children's Books` / speech,
         adult_books_vs_speech = `Adult Books` / speech)
```

## Child-directed speech vs. Adult speech

We first examine the keyness of words in child-directed speech vs. that in adult speech.
Here are the 10 words most over-represented in child-directed speech compared to adult movies:

```{r, echo=F}
# top 10
all_freq %>% arrange(desc(child_vs_adult_speech)) %>% head(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(child_vs_adult_speech)) %>% head(10) %>% kable(digits=2)
```


Here are the 10 words most under-represented in CHILDES, compared to adult movies:

```{r, echo=F}
all_freq %>% arrange(desc(child_vs_adult_speech)) %>% tail(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(child_vs_adult_speech)) %>% tail(10) %>% kable(digits=2)
```


## Children's books vs. adult speech

Here are the 10 words most over-represented in children's books compared to adult speech:

```{r, echo=F}
all_freq %>% arrange(desc(child_book_vs_adult_speech)) %>% head(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(child_book_vs_adult_speech)) %>% head(10) %>% kable(digits=2)
```


Here are the 10 words most under-represented in CHILDES compared to adult speech:

```{r, echo=F}
all_freq %>% arrange(desc(child_book_vs_adult_speech)) %>% tail(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(child_book_vs_adult_speech)) %>% tail(10) %>% kable(digits=2)
```

## Adult books vs. adult speech

For comparison, here are the 10 words most over-represented in adult books compared to adult speech:

```{r, echo=F}
all_freq %>% arrange(desc(adult_books_vs_speech)) %>% head(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(adult_books_vs_speech)) %>% head(10) %>% kable(digits=2)
```


and the 10 words most under-represented in adult books compared to adult speech:

```{r, echo=F}
all_freq %>% arrange(desc(adult_books_vs_speech)) %>% tail(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(adult_books_vs_speech)) %>% tail(10) %>% kable(digits=2)
```


# Keyness of CDI words vs. non-CDI words 

For just the `r nrow(all_freq)` words that occur in all four corpora:

```{r keyness-cdi-mean, eval=F, echo=F}
all_freq %>% group_by(on_cdi) %>%
  summarise(child_book_vs_adult_speech = mean(child_book_vs_adult_speech),
            child_vs_adult_speech = mean(child_vs_adult_speech),
            adult_books_vs_speech = mean(adult_books_vs_speech),
            n=n()) %>% kable(digits=2)
```

Now for the `r nrow(all_freq_smooth)` words appearing in any of the corpora, with Laplace-smoothed normalized frequencies:

```{r keyness-cdi-mean-smooth, eval=F, echo=F}
all_freq_smooth %>% group_by(on_cdi) %>%
  summarise(child_book_vs_adult_speech = mean(child_book_vs_adult_speech),
            child_vs_adult_speech = mean(child_vs_adult_speech),
            adult_books_vs_speech = mean(adult_books_vs_speech),
            n=n()) %>% kable(digits=2)
```

Below we show the average keyness of child-directed speech and children's books for CDI vs. non-CDI words, using adult speech as the reference corpus.
This is based on the words common to all corpora.

```{r, keyness-cdi-confint, echo=F, fig.width=8, fig.height=3.5}
ch_book <- all_freq %>% group_by(on_cdi) %>%
  tidyboot_mean(child_book_vs_adult_speech)

ch_speech <- all_freq %>% group_by(on_cdi) %>%
  tidyboot_mean(child_vs_adult_speech)

ad_speech <- all_freq %>% group_by(on_cdi) %>%
  tidyboot_mean(adult_books_vs_speech)

p1 <- ch_book %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Children's Books Keyness") #+ ylim(0,20)

p2 <- ch_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Child-directed Speech Keyness") #+ ylim(0,6)

p3 <- ad_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Adult Books Keyness") + ylim(0,5)

ggpubr::ggarrange(p1, p2, p3, nrow=1)
```

Now we do the same for the union of all words across the corpora (Laplace-smoothed).

```{r, keyness-cdi-confint-smooth, echo=F, fig.width=8, fig.height=3.5}
ch_book <- all_freq_smooth %>% group_by(on_cdi) %>%
  tidyboot_mean(child_book_vs_adult_speech)

ch_speech <- all_freq_smooth %>% group_by(on_cdi) %>%
  tidyboot_mean(child_vs_adult_speech)

ad_speech <- all_freq_smooth %>% group_by(on_cdi) %>%
  tidyboot_mean(adult_books_vs_speech)

p1 <- ch_book %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Children's Books Keyness") #+ ylim(0,20)

p2 <- ch_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Child-directed Speech Keyness") #+ ylim(0,6)

p3 <- ad_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Adult Books Keyness") #+ ylim(0,5)

ggpubr::ggarrange(p1, p2, p3, nrow=1)
```

## Predicting AoA

Which corpus best predicts words' AoA?
Which corpora contribute unique variance to predicting AoA?
(Does the book corpus interact with SES, since we expect high-SES parents read more to their children?)

```{r}
load("data/en_ws_production.Rdata")

# poor man's AoA
cdi_acc <- d_en_ws %>% group_by(definition, category, lexical_class) %>%
  summarise(mean_produces = mean(produces, na.rm=T)) 

d_age <- d_en_ws %>% left_join(d_demo %>% select(data_id, age)) %>%
  filter(!is.na(age)) %>%
  group_by(definition, category, lexical_class, age) %>%
  summarise(mean_produces = mean(produces, na.rm=T))

d_age %>% ggplot(aes(x=age, y=mean_produces, group=definition, color=lexical_class)) + 
  geom_line(alpha=.3) + theme_classic()
#d50pct <- d_age %>% filter(mean_produces < .55, mean_produces > .45)
# ToDo: get AoA model fits
```


## Other Ideas

- Does the mean IRT difficulty of CDI/non-CDI words systematically vary with the source?
- Use adult books as reference corpus for keyness metric (instad of subtitles)
