---
title: "Where do CDI words come from?"
author: "George & Georgia"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(glue)
library(wordbankr)
require(tidyverse)
require(here)
require(ggrepel)
require(kableExtra)
require(tidyboot)
require(readr)
require(tokenizers)
```


## Goal

Can we identify words on the CDI that are more bookish, speechy, or from TV? (Controlling for difficulty, as more bookish words are probably more difficult)

Using this distributional source information, can we find features of children (e.g., mother's education) that relate to knowledge of subsets of words (e.g. bookish words)?

To start, we will look at American English, before extending to British English and French.
We will begin with unlemmatized corpora, and disregard part-of-speech classification.

```{r load-data, echo=F, eval=F}
process_text <- function(path, source_name) {
  words = tokenize_words(read_file(path))
  tab <- table(words[[1]])
  wf <- data_frame(word = names(tab), word_count = as.numeric(tab)) %>%
    mutate(source = source_name,
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count)) %>%
    mutate(word = ifelse(word=="i", "I", ifelse(word=="i'll", "I'll", word))) %>%
    arrange(desc(word_count_norm)) %>%
    mutate(rank = 1:n())
  print(paste0("loaded ", nrow(wf), " word types (", sum(wf$word_count)," tokens)"))
  return(wf)
}

data_dir = "data/Charlesworth-Clean-data/"
adult_dat <- bind_rows(process_text(here(paste0(data_dir, "Adult_Books/gutenberg_corpus.txt")), "books"),
                       process_text(here(paste0(data_dir, "Adult_Speech/adult_speech_corpus.txt")), "speech")) 
# or lemmatized_adult_speech_corpus.txt
# loaded 827414 word types (35143617 tokens)
# loaded 27536 word types (3104328 tokens)


# combine the TV corpora
tv1 <- process_text(here(paste0(data_dir, "Adult_TV/pbs_adults_corpus.txt")), "tv1")
# loaded 45351 word types (4175570 tokens)
tv2 <- process_text(here(paste0(data_dir, "Adult_TV/simply_scripts_corpus.txt")), "tv2")
# loaded 103079 word types (2056384 tokens)
#tv1 %>% select(word, word_count) 

adult_tv <- full_join(tv1 %>% select(word, word_count), 
                      tv2 %>% select(word, word_count), by="word") %>%
  mutate(word_count.x = replace_na(word_count.x, 0),
         word_count.y = replace_na(word_count.y, 0),
         word_count = word_count.x + word_count.y) %>%
  select(word, word_count) %>%
  filter(word_count>1) %>% # hapaxes are mostly junk--phrases with spaces/punctuation removed
  mutate(source = "TV",
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count)) %>%
  mutate(word = ifelse(word=="i", "I", ifelse(word=="i'll", "I'll", word))) %>% # I'd I've..
  arrange(desc(word_count_norm)) %>%
  mutate(rank = 1:n())

adult_dat = bind_rows(adult_dat, adult_tv)

child_dat <- bind_rows(
  process_text(here(paste0(data_dir, "Child_Books/unlemmatized_child_books.txt")), "books"),
  process_text(here(paste0(data_dir, "Child_TV/childrens_tv_combined_corpus.txt")), "tv"),
  process_text(here(paste0(data_dir, "CHILDES clean text/corpus_parents.txt")), "speech")
  ) %>%
  filter(!is.element(word, c("d","m","s","t", "xxx", "ve", "ll", "n't", "rrb", "unc", "re"))) 
# loaded 42652 word types (4730867 tokens)
# loaded 84341 word types (6759928 tokens)
# loaded 38770 word types (5495648 tokens)


save(adult_dat, child_dat, file="data/Charlesworth-unlemmatized-counts.Rdata")
```

```{r load-orig-data, echo=F, message=F, warning=F}
# ToDo: remove book-reading corpora from CHILDES data!
# CHILDES corpus (hapaxes already removed, but 6295 word_count==2)
child_speech <- read_csv(here("data/childes_english_word_freq_cleaned_noHapaxes.csv")) %>% 
  select(-X1) %>%
  mutate(source = "CHILDES") %>%
#         word = tolower(word)) %>% 
#  mutate(word = ifelse(word=="i", "I", ifelse(word=="i'll", "I'll", word))) %>%
  arrange(desc(word_count)) %>%
  mutate(rank = 1:n())

#load("data/en_ws_production.Rdata")
#cdi_items = unique(d_en_ws$definition)

cdi_voc = subset(child_speech, on_cdi==1)$word # 657 / 680 -- should check other 23 words

# SUBTLEX-US subtitle word frequencies (adult speech standard), min freq = 2
adult_speech <- read_csv(here("data/SUBTLEX-US.csv")) %>% # 50.3 million words
  rename(word_count_norm = SUBTLWF, # frequency per million words
         word_count = SLUSfreq) %>%
  mutate(word = tolower(word)) %>%
  group_by(word) %>%
  summarise(word_count = sum(word_count)) %>%
  mutate(source = "SUBTLEX",
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count)) %>%
  mutate(word = ifelse(word=="i", "I", word)) %>%
  arrange(desc(word_count_norm)) %>%
  mutate(rank = 1:n()) %>%
  select(word, word_count, word_count_norm, prob, source, rank) %>%
  mutate(on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) # 610 CDI words

# SUBTLEX is missing all of the apostrophized words...let's use the Charlesworth corpus instead
load("data/Charlesworth-unlemmatized-counts.Rdata") 

adult_dat <- adult_dat %>% 
  mutate(on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) # 
table(adult_dat$on_cdi, adult_dat$source) 
# 638 CDI words in books, 618 in speech, 636 on TV

child_dat <- child_dat %>% 
  mutate(on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) 
table(child_dat$on_cdi, child_dat$source)
# 596 in books, 656 in speech, 652 on TV

# Google book frequencies (743.8 billion words) min freq = 100005
adult_books <- read.csv(here("data/google-books-common-words.txt"), sep='\t') %>%
  mutate(word = tolower(word),
         word = ifelse(word=="i", "I", word),
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count),
         source = "Adult Books") %>%
  arrange(desc(word_count)) %>%
  mutate(rank = 1:n(),
         on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) # 643

# min freq = 1 (2548, but mostly real words)
child_books <- read.csv(here("data/Montag-book-corpus/100out.txt"), sep=' ') %>% 
  mutate(word = ifelse(word=="i", "I", word),
         word_count_norm = word_count * (1e6 / sum(word_count)), # count per million tokens
         prob = word_count / sum(word_count),
         source = "Children's Books"
  ) %>%
  arrange(desc(word_count)) %>%
  mutate(rank = 1:n(),
         on_cdi = ifelse(is.element(word, cdi_voc), 1, 0)) 
```

Our data sources:

- Adult speech: `r nrow(adult_speech)` types, `r sum(adult_speech$word_count)` tokens from the SUBTLEX corpus (`r sum(adult_speech$on_cdi)` CDI words)
- Children speech: `r nrow(child_speech)` types, `r sum(child_speech$word_count)` tokens from the CHILDES corpus (`r sum(child_speech$on_cdi)` CDI words)
- Adult books: `r nrow(adult_books)` types, `r sum(adult_books$word_count)` tokens from the Google books corpus
- Children's books: `r nrow(child_books)` types, `r sum(child_books$word_count)` tokens from the CHILDES corpus (`r sum(child_books$on_cdi)` CDI words)


## Normalize Word Frequencies

We will calculate keyness scores for each word, i.e. the ratio of normalized frequency in focus corpus to normalized frequency in a reference corpus.
For now, we will use the subset of words that are found in all four corpora (N=4229), but we may consider following Dawson et al. (2021) and adding a constant (e.g., 10) to all normalized frequencies in every corpus in order to not eliminate the bulk of words that do not appear in the smaller corpora (which are the child-directed corpora).
<!-- "Given the problem of calculating ratios for words occurring in the focus corpus, but not at all in the reference corpus, we added a constant of 10 to all normalised frequencies before calculating keyness. We selected this value as the constant because it focuses the keyword analysis on the lower end of the frequency spectrum (Kilgarriff, 2009), which we considered to be important when identifying the words that children were unlikely to encounter in everyday conversation, but which they would experience through regular exposure to book language." --> 


### Child-directed Speech vs. Books

```{r keyness-childes-vs-montag, echo=F}
# CHILDES and Montag books
ch_freq_long <- rbind(child_speech, child_books) %>%
  select(word, source, on_cdi, word_count_norm, word_count) %>%
  filter(!is.element(word, c("d","m","s","t", "xxx", "ve", "ll", "n't", "rrb", "unc", "re"))) 
# equivalent to child_dat, which is based on Charlesworth corpora

# wide - no smoothing, only keep subset of 4611 words in all corpora
ch_freq <- ch_freq_long %>% select(-word_count) %>%
  pivot_wider(names_from = source, values_from = word_count_norm) %>%
  filter(!is.na(`Children's Books`), !is.na(CHILDES)) %>%
  mutate(ch_book_vs_speech = `Children's Books` / CHILDES,
         prop_booky = `Children's Books` / (`Children's Books` + CHILDES)) 

# Laplace smoothing, alpha=10, keep all 123060 words in any corpus
ch_freq_smooth <- ch_freq_long %>% 
  mutate(word_count_norm_smooth = word_count_norm + 10) %>%
  pivot_wider(id_cols = c(word, on_cdi), names_from = source, values_from = word_count_norm_smooth, values_fill=10) %>% 
  filter(!is.na(`Children's Books`), !is.na(CHILDES)) %>%
  mutate(ch_book_vs_speech = `Children's Books` / CHILDES,
         prop_booky = `Children's Books` / (`Children's Books` + CHILDES))
```

```{r keyness-charlesworth-corpora, echo=F}
# wide - no smoothing, only keep subset of 12855 words in all corpora
ch_freq_charles <- child_dat %>% select(-word_count) %>%
  pivot_wider(id_cols = c(word, on_cdi), names_from = source, values_from = word_count_norm) %>%
  filter(!is.na(books), !is.na(speech), !is.na(tv)) %>%
  mutate(ch_book_vs_speech = books / speech,
         prop_booky = books / (books + speech)) 

# Laplace smoothing, alpha=10, keep all 124036 words in any corpus
ch_freq_smooth_charles <- child_dat %>% 
  mutate(word_count_norm_smooth = word_count_norm + 10) %>%
  pivot_wider(id_cols = c(word, on_cdi), names_from = source, values_from = word_count_norm_smooth, values_fill=10) %>% 
  filter(!is.na(books), !is.na(speech), !is.na(tv)) %>%
  mutate(ch_book_vs_speech = books / speech,
         prop_booky = books / (books + speech))
```

### Most Child Booky Words

```{r}
#ch_freq %>% arrange(desc(ch_book_vs_speech)) %>% head(10) %>% kable(digits=2)
#ch_freq_smooth %>% arrange(desc(ch_book_vs_speech)) %>% head(10) %>% kable(digits=2)

p1 <- ch_freq %>% mutate(Word = ifelse(on_cdi==1, "CDI", "Non-CDI")) %>%
  ggplot(aes(x=CHILDES, y=`Children's Books`, color=Word)) + 
  geom_point(alpha=.3) + theme_classic() + geom_smooth(method='lm') +
  scale_x_log10() + scale_y_log10() + ggtitle("Raw Frequencies (intersection)")

p2 <- ch_freq_smooth %>% mutate(Word = ifelse(on_cdi==1, "CDI", "Non-CDI")) %>%
  ggplot(aes(x=CHILDES, y=`Children's Books`, color=Word)) + 
  geom_point(alpha=.3) + theme_classic() + geom_smooth(method='lm') +
  scale_x_log10() + scale_y_log10() + ggtitle("Smoothed Frequencies (union)")

ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
```


```{r}
cor(subset(ch_freq, on_cdi==1)$CHILDES, subset(ch_freq, on_cdi==1)$`Children's Books`) # .75
cor(subset(ch_freq, on_cdi==0)$CHILDES, subset(ch_freq, on_cdi==0)$`Children's Books`) # .42
```

Same, but with Charlesworth corpora

```{r}
p1 <- ch_freq_charles %>% mutate(Word = ifelse(on_cdi==1, "CDI", "Non-CDI")) %>%
  ggplot(aes(x=speech, y=books, color=Word)) + 
  geom_point(alpha=.3) + theme_classic() + geom_smooth(method='lm') +
  scale_x_log10() + scale_y_log10() + ggtitle("Raw Frequencies (intersection)")

p2 <- ch_freq_smooth_charles %>% mutate(Word = ifelse(on_cdi==1, "CDI", "Non-CDI")) %>%
  ggplot(aes(x=speech, y=books, color=Word)) + 
  geom_point(alpha=.3) + theme_classic() + geom_smooth(method='lm') +
  scale_x_log10() + scale_y_log10() + ggtitle("Smoothed Frequencies (union)")

ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
```


### Which CDI words are more booky/speechy?

```{r, fig.width=10, fig.height=5}
p1 <- ch_freq_smooth %>% filter(on_cdi==1) %>%
  ggplot(aes(x=CHILDES, y=`Children's Books`)) + 
  geom_point(alpha=.3) + theme_classic() + 
  scale_x_log10() + scale_y_log10() +
  geom_text_repel(aes(label=word)) +
  geom_abline(intercept = 0, slope = 1, linetype="dashed") +
  ggtitle("CHILDES vs. Montag book corpus")
  #geom_text(data=subset(ch_freq_smooth, on_cdi==1 & (wt > 4 | mpg > 25)), aes(label=name))

p2 <- ch_freq_smooth_charles %>% filter(on_cdi==1) %>%
  ggplot(aes(x=speech, y=books)) + 
  geom_point(alpha=.3) + theme_classic() + 
  scale_x_log10() + scale_y_log10() +
  geom_text_repel(aes(label=word)) + xlab("CHILDES") + 
  geom_abline(intercept = 0, slope = 1, linetype="dashed") +
  ggtitle("CHILDES vs. FB Children's Books")

p3 <- ch_freq_smooth_charles %>% filter(on_cdi==1) %>%
  ggplot(aes(x=speech, y=tv)) + 
  geom_point(alpha=.3) + theme_classic() + 
  scale_x_log10() + scale_y_log10() +
  geom_text_repel(aes(label=word)) + ylab("Children's TV and Movies") + 
  geom_abline(intercept = 0, slope = 1, linetype="dashed") +
  ggtitle("CHILDES vs. Children's Movies")

# merge in lexical_class and color points by it?

ggpubr::ggarrange(p1, p2, p3, nrow=1, common.legend = T)
ggsave("CHILDES_smoothed_norm_freqs_vs_books_TV.pdf", width=12, height=6)
```



```{r}
# holds even if we filter out many low frequency words
ch_key <- ch_freq %>% #filter(CHILDES>1, `Children's Books`>1) %>%
  group_by(on_cdi) %>%
  tidyboot_mean(ch_book_vs_speech)

ch_key_smooth <- ch_freq_smooth %>% 
  group_by(on_cdi) %>%
  tidyboot_mean(ch_book_vs_speech)

p1 <- ch_key %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Children's Book Keyness") + xlab("")

p2 <- ch_key_smooth %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Children's Book Keyness") + xlab("")

ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
```

```{r}
ch_booky <- ch_freq %>% group_by(on_cdi) %>%
  tidyboot_mean(prop_booky)

ch_booky_smooth <- ch_freq_smooth %>% group_by(on_cdi) %>%
  tidyboot_mean(prop_booky)

p1 <- ch_booky %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Proportion of Book Occurrences") 

p2 <- ch_booky_smooth %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Proportion of Book Occurrences")

ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
```

## Booky vs. Speechy vs. TV Words

Table based on Charlesworth corpora

```{r}
ch_freq_smooth_charles %>% filter(on_cdi==1) %>% 
  select(-ch_book_vs_speech) %>%
  DT::datatable() %>%
  DT::formatRound(columns=c('books','tv','speech'), digits=0) %>%
  DT::formatPercentage(columns=c('prop_booky'), digits=0)
```


## Predicting AoA

Which corpus best predicts words' AoA?
Which corpora contribute unique variance to predicting AoA?
(Does the book corpus interact with SES, since we expect high-SES parents read more to their children?)

```{r}
load("data/en_ws_production.Rdata")


dd <- ch_freq_smooth_charles %>% filter(on_cdi==1) %>% 
  select(-ch_book_vs_speech)
  
#### add aoas
#walk(list.files(".", pattern = "aoa_functions.R$", full.names = TRUE), source)
#wb_data <- load_wb_data("English (American)")
#aoas <- fit_aoas(wb_data)


summary(dd)

# poor man's AoA
cdi_acc <- d_en_ws %>% group_by(definition, category, lexical_class) %>%
  summarise(mean_produces = mean(produces, na.rm=T)) %>%
  mutate(word = case_when(definition=="a lot" ~ "lot",
                          definition=="all gone" ~ "gone",
                          #definition=="babysitter's name" ~ "babysitter",
                          definition=="buttocks/bottom*" ~ "butt",
                          definition=="call (on phone)" ~ "call",
                          definition=="can (auxiliary)" ~ "can",
                          definition=="can (object)" ~ "can",
                          definition=="chicken (animal)" ~ "chicken",
                          definition=="chicken (food)" ~ "chicken",
                          definition=="clean (action)" ~ "clean",
                          definition=="clean (description)" ~ "clean",
                          definition=="church*" ~ "church", # add temple, synagogue..?
                          definition=="daddy*" ~ "daddy",
                          definition=="mommy*" ~ "mommy",
                          definition=="grandma*" ~ "grandma",
                          definition=="grandpa*" ~ "grandpa",
                          definition=="vagina*" ~ "vagina",
                          definition=="penis*" ~ "penis",
                          definition=="drink (beverage)" ~ "drink",
                          definition=="drink (action)" ~ "drink",
                          definition=="did/did ya" ~ "did",
                          definition=="dress (object)" ~ "dress",
                          definition=="dry (action)" ~ "dry",
                          definition=="dry (description)" ~ "dry",
                          definition=="baa baa" ~ "baa",
                          definition=="choo choo" ~ "choo",
                          definition=="woof woof" ~ "woof",
                          definition=="yum yum" ~ "yum",
                          definition=="fish (animal)" ~ "fish",
                          definition=="fish (food)" ~ "fish",
                          definition=="gas station" ~ "gas", # or station? or average?
                          definition=="work (action)" ~ "work",
                          definition=="work (place)" ~ "work",
                          definition=="water (beverage)" ~ "water",
                          definition=="water (not beverage)" ~ "water",
                          definition=="wanna/want to" ~ "wanna", # or want
                          definition=="watch (action)" ~ "watch",
                          definition=="watch (object)" ~ "watch",
                          definition=="TV" ~ "tv",
                          definition=="washing machine" ~ "washing",
                          definition=="lawn mower" ~ "mower",
                          definition=="soda/pop" ~ "soda",
                          definition=="swing (action)" ~ "swing",
                          definition=="swing (object)" ~ "swing",
                          definition=="go potty" ~ "potty",
                          definition=="gonna/going to" ~ "gonna", # search CHILDES
                          definition=="gotta/got to" ~ "gotta",
                          definition=="little (description)" ~ "little",
                          definition=="next to" ~ "next",
                          definition=="hafta/have to" ~ "hafta",
                          definition=="french fries" ~ "fries",
                          definition=="need/need to" ~ "need",
                          definition=="inside/in" ~ "in", # also inside
                          definition=="orange (description)" ~ "orange",
                          definition=="orange (food)" ~ "orange",
                          definition=="on top of" ~ "top",
                          definition=="owie/boo boo" ~ "ouch",
                          definition=="potato chip" ~ "chip",
                          definition=="quack quack" ~ "quack",
                          definition=="tissue/kleenex" ~ "tissue",
                          definition=="shh/shush/hush" ~ "shh",
                          definition=="slide (action)" ~ "slide",
                          definition=="slide (object)" ~ "slide",
                          definition=="teddybear" ~ "teddy",
                          definition=="thank you" ~ "thanks",
                          definition=="toy (object)" ~ "toy",
                          definition=="try/try to" ~ "try",
                          definition=="turn around" ~ "turn",
                          definition=="TV" ~ "tv", # or television
                          definition=="uh oh" ~ "uhoh",
                          TRUE ~ definition)) %>%
  filter(!is.element(definition, c("babysitter's name", "child's own name", "gonna get you!", "give me five!", "pet's name", "so big!", "this little piggy")))
# remove some words we can't match

itdat <- left_join(cdi_acc, dd)
# need to fix all the parenthetical / starred / slashed items
itdat[which(!complete.cases(itdat)),]


ddd <- itdat %>% filter(!is.na(on_cdi)) 

summary(lm(mean_produces ~ prop_booky, data=ddd)) # r^2 = .22; more booky = harder

ddd$books = scale(log(ddd$books), center=F)[,1]
ddd$tv = scale(log(ddd$tv), center=F)[,1]
ddd$speech = scale(log(ddd$speech), center=F)[,1]

# we should tack on adult_books
cor.test(itdat$books, itdat$speech) # .73
cor.test(itdat$tv, itdat$speech) # .83
cor.test(itdat$tv, itdat$books) # .94
# Books and TV are most correlated; books and speech least correlated

# correlations change if we scale and log the frequencies...
cor.test(ddd$books, ddd$speech) # .81
cor.test(ddd$tv, ddd$speech) # .86
cor.test(ddd$tv, ddd$books) # .87

# with all 3 sources, only speech and books are significant
summary(lm(mean_produces ~ books + speech + tv, data=ddd)) # 

summary(lm(mean_produces ~ books + tv + speech, data=ddd))
summary(lm(mean_produces ~ books + speech, data=ddd))
```


## Predict Booky Vocabulary per child by Mother Education

(also try ses_group)

```{r}
# let's take the 200 bookiest CDI items and look at relation of subscore to mom_ed
booky_items <- itdat %>% arrange(desc(prop_booky)) %>% head(200)

samp <- d_demo %>% filter(!is.na(mom_ed)) # 2773

booky_scores <- d_en_ws %>% filter(is.element(definition, booky_items$definition)) %>%
  group_by(data_id) %>% summarise(booky_production = sum(produces))

# most children get 0 booky words (they're hard)
# hist(booky_scores$booky_production)
samp <- left_join(samp, booky_scores)

#AoA ~ book_freq * mom_ed + spoken_freq * mom_ed

summary(lm(production ~ age, data=samp)) # .465
summary(lm(production ~ age + mom_ed, data=samp)) # r^2 = .477

summary(lm(booky_production ~ age , data=samp)) # r^2 = .452
summary(lm(booky_production ~ age + mom_ed, data=samp)) # .462

samp %>% 
  mutate(nonbooky_production = production - booky_production) %>%
  ggplot(aes(x=booky_production, y=nonbooky_production, color=mom_ed, shape=mom_ed)) +
  geom_point(alpha=.3) + theme_classic() + geom_smooth()

d_age <- d_en_ws %>% left_join(d_demo %>% select(data_id, age)) %>%
  filter(!is.na(age)) %>%
  group_by(definition, category, lexical_class, age) %>%
  summarise(mean_produces = mean(produces, na.rm=T))

d_age %>% ggplot(aes(x=age, y=mean_produces, group=definition, color=lexical_class)) + 
  geom_line(alpha=.3) + theme_classic()
#d50pct <- d_age %>% filter(mean_produces < .55, mean_produces > .45)
# ToDo: get AoA model fits
```


## Per-child, per-item mixed effects

produces ~ book_freq * mom_ed + speech_freq * mom_ed + (1|item) + (1|child)
produces ~ lexical_class * book_freq * mom_ed + lexical_class * speech_freq * mom_ed + (1|item) + (1|child)

```{r}
d_samp <- d_en_ws %>% filter(is.element(data_id, samp$data_id)) %>%
  left_join(samp %>% select(data_id, age, production, mom_ed, ses_group)) %>% # vocab? booky_production
  left_join(itdat %>% select(definition, lexical_class, books, tv, speech, prop_booky))

require(lme4)
require(lmerTest)
require(ggeffects)
require(ggpubr)

d_samp <- d_samp %>% mutate(age_sc = scale(age), 
                            books_sc = scale(log(books)),
                            tv_sc = scale(log(tv)),
                            speech_sc = scale(log(speech)),
                            prop_booky_sc = scale(log(prop_booky)),
                            mom_ed_sc = scale(as.numeric(mom_ed)))

m1 <- glmer(produces ~ age_sc + books_sc * mom_ed_sc + speech_sc * mom_ed_sc + (1|item_id) + (1|data_id), family=binomial, data=d_samp)
summary(m1)
anova(m1)

m1_age_mom_ed <- ggemmeans(m1, c("age_sc", "mom_ed_sc"))
m1_speech_mom_ed <- ggemmeans(m1, c("mom_ed_sc","speech_sc"))
m1_books_mom_ed <- ggemmeans(m1, c("mom_ed_sc","books_sc"))

ggarrange(plot(m1_age_mom_ed), plot(m1_speech_mom_ed), plot(m1_books_mom_ed), nrow=1)


m1pred <- ggpredict(m1)
m1eff <- ggeffect(m1)

m2 <- glmer(produces ~ age_sc + lexical_class * books_sc * mom_ed_sc + lexical_class * speech_sc * mom_ed_sc + (1|item_id) + (1|data_id), family=binomial, data=d_samp)
summary(m2)

m2book <- ggpredict(m2, terms=c("mom_ed_sc","lexical_class","books_sc"))
m2speech <- ggpredict(m2, terms=c("mom_ed_sc","lexical_class","speech_sc"))


ggarrange(plot(m2book), plot(m2speech), nrow=1, common.legend = T)
#m3 <- lmer(produces ~ age + mom_ed * prop_booky * lexical_class, data=d_samp)
# somehow control for word difficulty: 
# utterance length, word length, and/or morphological complexity?

save(m1, m2, file="data/model_fits.Rdata")
```




## Also try same regressions controlling for Google books frequency (reference corpus) 


### Comparing to Adult Speech

For our reference corpus, we will use adult speech (movie subtitles), as this is the target language distribution that children will eventually learn.
(Although we could use child-directed speech, as that is what is given to children, or Google book frequency, which could be considered the epitome of an 'educated' distribution.)

```{r keyness-subtlex, echo=F, eval=F}
all_freq_long <- rbind(child_speech, adult_speech, child_books, adult_books) %>%
  select(word, source, on_cdi, word_count_norm) %>%
  filter(!is.element(word, c("d","m","s","t", "xxx"))) 

# wide - no smoothing, only keep subset of words in all corpora
all_freq <- all_freq_long %>%
  pivot_wider(names_from = source, values_from = word_count_norm) %>%
  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(SUBTLEX), !is.na(`Adult Books`)) %>%
  mutate(child_vs_adult_speech = CHILDES / SUBTLEX, 
         child_book_vs_adult_speech = `Children's Books` / SUBTLEX,
         adult_books_vs_speech = `Adult Books` / SUBTLEX)
         #ch_book_ad_book_ratio = `Children's Books` / `Adult Books`,
         #ch_book_ad_book_ratio = `Children's Books` / CHILDES) # are children's books like adult books, or like children's speech?

# Laplace smoothing, alpha=1, keep all 123060 words in any corpus
all_freq_smooth <- all_freq_long %>% 
  mutate(word_count_norm_smooth = word_count_norm + 1) %>%
  pivot_wider(id_cols = c(word, on_cdi), names_from = source, values_from = word_count_norm_smooth, values_fill=1) %>% 
  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(SUBTLEX), !is.na(`Adult Books`)) %>%
  mutate(child_vs_adult_speech = CHILDES / SUBTLEX, 
         child_book_vs_adult_speech = `Children's Books` / SUBTLEX,
         adult_books_vs_speech = `Adult Books` / SUBTLEX)
```

Non-SUBTLEX adult speech (Charlesworth corpus):

```{r keyness-charlesworth, echo=F, eval=F}
all_freq_long <- rbind(child_speech, adult_speech2, child_books, adult_books) %>%
  select(word, source, on_cdi, word_count_norm) %>%
  filter(!is.element(word, c("d","m","s","t", "xxx", "child's own name"))) 

# wide - no smoothing, only keep subset of 3977 words in all corpora
all_freq <- all_freq_long %>%
  pivot_wider(names_from = source, values_from = word_count_norm) %>%
  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(speech), !is.na(`Adult Books`)) %>%
  mutate(child_vs_adult_speech = CHILDES / speech, 
         child_book_vs_adult_speech = `Children's Books` / speech,
         adult_books_vs_speech = `Adult Books` / speech)

# Laplace smoothing, alpha=10, keep all 115597 words in any corpus
all_freq_smooth <- all_freq_long %>% 
  mutate(word_count_norm_smooth = word_count_norm + 10) %>%
  pivot_wider(id_cols = c(word, on_cdi), names_from = source, values_from = word_count_norm_smooth, values_fill=10) %>% 
  filter(!is.na(`Children's Books`), !is.na(CHILDES), !is.na(speech), !is.na(`Adult Books`)) %>%
  mutate(child_vs_adult_speech = CHILDES / speech, 
         child_book_vs_adult_speech = `Children's Books` / speech,
         adult_books_vs_speech = `Adult Books` / speech)
```

## Child-directed speech vs. Adult speech

We first examine the keyness of words in child-directed speech vs. that in adult speech.
Here are the 10 words most over-represented in child-directed speech compared to adult movies:

```{r, echo=F, eval=F}
# top 10
all_freq %>% arrange(desc(child_vs_adult_speech)) %>% head(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(child_vs_adult_speech)) %>% head(10) %>% kable(digits=2)
```


Here are the 10 words most under-represented in CHILDES, compared to adult movies:

```{r, echo=F, eval=F}
all_freq %>% arrange(desc(child_vs_adult_speech)) %>% tail(10) %>% kable(digits=2)
all_freq_smooth %>% arrange(desc(child_vs_adult_speech)) %>% tail(10) %>% kable(digits=2)
```


Below we show the average keyness of child-directed speech and children's books for CDI vs. non-CDI words, using adult speech as the reference corpus.
This is based on the words common to all corpora.

```{r, keyness-cdi-confint, echo=F, eval=F, fig.width=8, fig.height=3.5}
ch_book <- all_freq %>% group_by(on_cdi) %>%
  tidyboot_mean(child_book_vs_adult_speech)

ch_speech <- all_freq %>% group_by(on_cdi) %>%
  tidyboot_mean(child_vs_adult_speech)

ad_speech <- all_freq %>% group_by(on_cdi) %>%
  tidyboot_mean(adult_books_vs_speech)

p1 <- ch_book %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Children's Books Keyness") #+ ylim(0,20)

p2 <- ch_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Child-directed Speech Keyness") #+ ylim(0,6)

p3 <- ad_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Adult Books Keyness") + ylim(0,5)

ggpubr::ggarrange(p1, p2, p3, nrow=1)
```

Now we do the same for the union of all words across the corpora (Laplace-smoothed).

```{r, keyness-cdi-confint-smooth, echo=F, eval=F, fig.width=8, fig.height=3.5}
ch_book <- all_freq_smooth %>% group_by(on_cdi) %>%
  tidyboot_mean(child_book_vs_adult_speech)

ch_speech <- all_freq_smooth %>% group_by(on_cdi) %>%
  tidyboot_mean(child_vs_adult_speech)

ad_speech <- all_freq_smooth %>% group_by(on_cdi) %>%
  tidyboot_mean(adult_books_vs_speech)

p1 <- ch_book %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Children's Books Keyness") #+ ylim(0,20)

p2 <- ch_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Child-directed Speech Keyness") #+ ylim(0,6)

p3 <- ad_speech %>% mutate(CDI = ifelse(on_cdi==1, "CDI Words", "non-CDI Words")) %>%
  ggplot(aes(x=CDI, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper)) +
  theme_classic() + ylab("Adult Books Keyness") #+ ylim(0,5)

ggpubr::ggarrange(p1, p2, p3, nrow=1)
```


## Other Ideas

- Does the mean IRT difficulty of CDI/non-CDI words systematically vary with the source?
- Use adult books as reference corpus for keyness metric (instad of subtitles)
