---
title: "Identifying the distributional sources of children's early vocabulary"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf George Kachergis* (kachergis@stanford.edu)} \\ Department of Psychology, Stanford University \\ Stanford, CA 94305 USA
    \AND {\large \bf Georgia Loukatou (@stanford.edu)} \\ Department of Psychology, Stanford University \\ Stanford, CA 94305 USA}

abstract: >
    Children's early vocabulary learning must to a large extent be driven by the prevalence 
    of words: they can't learn a word if they haven't heard it. Indeed, previous research 
    has found that higher word frequency is a good predictor of earlier learning. However,
    
    
keywords: >
    early language learning; CDI; vocabulary development.
    
output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(here)
```

# Introduction

Word usage varies significantly by context: you don't speak to your boss the same way as you do to your dog.

Frequency matters for children's language learning
- ambridge 
- dale goodman li etc. 

But - not all frequencies created equal
- books vs. speech vs. etc. 
- montag 
- nation paper

SES variation in register, language source

Our goals
- examine shared and unique variance in frequency across sources 
- consider relation with learning outcomes
- consider relation to SES (momed)

# Analysis 1: frequency components
- french and english
- PCA, show words that pop out as relatively more speech/booky, kid/adult
- predict kuperman aoa? (maybe)

# Analysis 2: predicting aoa 
- french and english
- aoa regressions - specific effects of bookiness/kidiness & interactions

# Analysis 3
- english
- does relative proportion bookines interaction with momed

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=4.5, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
#img <- png::readPNG("figs/walrus.png")
#grid::grid.raster(img)
knitr::include_graphics("../CHILDES_smoothed_norm_freqs_vs_books_TV.pdf")
```

## One-column images

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```


## R Plots

You can use R chunks directly to plot graphs. And you can use latex floats in the
fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**


## Tables

Number tables consecutively; place the table number and title (in
10 point) above the table with one line space above the caption and
one line space below it, as in Table 1. You may float
tables to the top or bottom of a column, set wide tables across both
columns.

You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                       caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
